Forecasting the 2024 U.S. Presidential Election: An Analysis of Battleground States

### 2024-11-01 paper/paper.qmd
remove figure title for figure 5

# Plotting
ggplot(filtered_data, aes(x = as.Date(end_date), y = pct, color = candidate_name)) +
  geom_point(alpha = 0.3, size = 1.5) +
  geom_smooth(method = "loess", se = TRUE, span = 0.2) +
  scale_color_manual(values = c("Kamala Harris" = "steelblue", "Donald Trump" = "indianred")) +
  labs(x = "Date", y = "Support (%)", title = "Support Trends for Kamala Harris and Donald Trump") +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 0),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )

>>>>

# Plotting
ggplot(filtered_data, aes(x = as.Date(end_date), y = pct, color = candidate_name)) +
  geom_point(alpha = 0.3, size = 1.5) +
  geom_smooth(method = "loess", se = TRUE, span = 0.2) +
  scale_color_manual(values = c("Kamala Harris" = "steelblue", "Donald Trump" = "indianred")) +
  labs(x = "Date", y = "Support (%)") +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 0),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )
